Probing internal structure of distant quasars using Microlensing

### 2013-11-19 paper1/ms.tex
paper1 added
ms.tex changed

%\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
%Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^3$\\
%$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
%$^2${University of Heidelberg, Germany}
%}

@@

>>>>

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^3$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

\input{fitting}
